Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-11-18 paper/ms.tex
editing the discussion

In the previous Section we started by matching the rough numbers for the
galaxy surface number density. This sets the median mass of all
successful models to the broad range $(10^{10}$-$10^{12})$ \hMsun for
$M_{\rm min}$ and $M_{\rm max}$. Then we included additional criteria on the
number of mock surveys that must be consistent observations
and the information from the angular correlation function, reducing
the number of feasible models. We ended up with $23$ models out of
the initial $9000$ possible combination of parameters.

Now we define the halo mass range $\Delta M=\log_{10}M_{\rm max} -
\log_{10}M_{\rm  min}$, to use it together with the occupation
fraction, $f_{\rm occ}$, and the minimum mass $M_{\rm min}$ to
classify all the successful models into two families:

\begin{itemize}
\item[(1)] Low $f_{\rm occ}\leq 0.3$, $M_{\rm min}\leq 10^{10.8}\hMsun$ and low $\Delta M\leq 1.0$
  dex: 12 models. 
\item[(2)] High $f_{\rm occ}> 0.3$, $M_{\rm min}\geq 10^{10.8}\hMsun$ and
  low $\Delta M\leq 1.0$: 11 models 
\end{itemize}
%
The full list of parameter in the two families is summarized in Table
\ref{table:firstfamily} and Table \ref{table:secondfamily}. We do not
have a clear majority of any family. This leads us to the following
two conclusions. First, the occupation fraction cannot be constrained
based on clustering analysis. Second, the halos hosting LAEs have a
narrow mass range.

The existence of a narrow mass range for halo masses has different
possible explanations. A cut at the low mass end, $M_{\rm min}$, can be
interpreted in terms of the minimal halo star formation rate needed to
produce the \ly luminosity needed to be above a given detection
threshold.  However, under the reasonable assumption of star formation
rate increasing with halo mass, the cut at higher halo masses $M_{\rm
  max}$requires a different justification. There are two complementary physical
scenarios that could provide it.

>>>>

We end up with $XX$ models, out of $9000$ initial guesses, consistent
with observations. In order to discuss these results we now
define the halo mass range $\Delta M=\log_{10}M_{\rm max} -
\log_{10}M_{\rm  min}$, to use it together with the occupation
fraction, $f_{\rm occ}$, and the minimum mass $M_{\rm min}$ to
classify all the successful models into two families:

\begin{itemize}
\item[(1)] Low $f_{\rm occ}\leq 0.3$, $M_{\rm min}\leq 10^{10.8}\hMsun$ and low $\Delta M\leq 1.0$
  dex: XX models. 
\item[(2)] High $f_{\rm occ}> 0.3$, $M_{\rm min}\geq 10^{10.8}\hMsun$ and
  low $\Delta M\leq 1.0$: XX models 
\end{itemize}
%
A complete parameter list is presented in Table
\ref{table:firstfamily} and Table \ref{table:secondfamily}. There are
two interesting feature in these families. First, the occupation
fraction can take any value from $0.1$ to $1.0$. Second, the halos
hosting LAEs all have a narrow mass range $\Delta M\leq 1.0$.

{\bf The existence of models with high occupation fractions $f_{\rm
    occ}>0.3$ is unexpected from previous clustering analysis that do
  not take  account the effect of cosmic variance in the same way we
  propose in this \documentname. It seems that taking explicitly into
  account  effect hinders the possibility of constraining the LAEs
  occupation fraction.}

{\bf This challenge can be tracked to the uncertainty in the minimum
  halo mass. Within out framework, high occupation fraction are
  allowed because there are models where the minimum mass for hosting
  observable LAEs is larger than $10^{10.8}$\hMsun, which are fully
  consistent with the observational constraints.}

{\bf On the other hand, a robust conclusion is that all
possible models have narrow mass range regardless of the occupation
fraction.}

...A cut at the low mass end, $M_{\rm min}$, can be
interpreted in terms of the minimal halo star formation rate needed to
produce the \ly luminosity needed to be above a given detection
threshold.  However, under the reasonable assumption of star formation
rate increasing with halo mass, the cut at higher halo masses $M_{\rm
  max}$requires a different justification. There are two complementary physical
scenarios that could provide it.
